Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/compilation.tex
edit to 5.3 intro to cut mention of vendor specific config translation
clarify about our implementation

We handle these challenges by breaking compilation into multiple stages and developing efficient algorithms for each (See Figure~\ref{fig:pipeline}). The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation. To make configurations more readable for human operators, and to reduce the size of the resulting configurations, the \sysname compiler makes several passes over the ABGP form. Finally, vendor-specific adaptors can translate from ABGP to concrete device configurations.

@@

The final stages of compilation translate policies from PGIR to a  vendor-neutral abstraction of BGP (ABGP) and then from ABGP to actual device configurations.

>>>>

We handle these challenges by breaking compilation into multiple stages and developing efficient algorithms for each (See Figure~\ref{fig:pipeline}). The first stage of the pipeline involves simple rewriting rules and substitutions from the FE to the core Regular Intermediate Representation (RIR). Policies in RIR are checked for well-formedness (\EG, never constraining traffic that does not enter the network), before being combined with the network topology to obtain the Product Graph Intermediate Representation (PGIR). The PGIR is a data representation that compactly captures the flow of BGP announcements subject to the policy and topology restrictions. We develop efficient algorithms that operate over the PGIR to ensure policy compliance under failures, avoid BGP instability, and prevent aggregation-induced black holes. Once the compiler determines that the PGIR is safe, it translates it to an abstract BGP (ABGP) representation. Our current \sysname compiler produces ABGP configurations, however vendor-specific adaptors to translate from ABGP to concrete device configurations could easily be added.

@@

The final stage of our compiler translates policies from PGIR to a vendor-neutral abstraction of BGP (ABGP).
% and then from ABGP to actual device configurations.
